Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-23 cordillera-cycle.tex
Rev. Marshall: add references.

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\bibitem[{Fisher et~al.(2008)Fisher, Osterberg, Dyke, Dahl-Jensen, Demuth, Zdanowicz, Bourgeois, Koerner, Mayewski, Wake, Kreutz, Steig, Zheng, Yalcin, Goto-Azuma, Luckman, and Rupper}]{Fisher.etal.2008}
Fisher, D., Osterberg, E., Dyke, A., Dahl-Jensen, D., Demuth, M., Zdanowicz, C., Bourgeois, J., Koerner, R.~M., Mayewski, P., Wake, C., Kreutz, K., Steig, E., Zheng, J., Yalcin, K., Goto-Azuma, K., Luckman, B., and Rupper, S.: The Mt Logan Holocene--late Wisconsinan isotope record: tropical Pacific--Yukon connections, The Holocene, 18, 667--677,
doi:\href{http://dx.doi.org/10.1177/0959683608092236}{10.1177/0959683608092236}, 2008.

\bibitem[{Fisher et~al.(2004)Fisher, Wake, Kreutz, Yalcin, Steig, Mayewski, Anderson, Zheng, Rupper, Zdanowicz, Demuth, Waszkiewicz, Dahl-Jensen, Goto-Azuma, Bourgeois, Koerner, Sekerka, Osterberg, Abbott, Finney, and Burns}]{Fisher.etal.2004}
Fisher, D.~A., Wake, C., Kreutz, K., Yalcin, K., Steig, E., Mayewski, P., Anderson, L., Zheng, J., Rupper, S., Zdanowicz, C., Demuth, M., Waszkiewicz, M., Dahl-Jensen, D., Goto-Azuma, K., Bourgeois, J.~B., Koerner, R.~M., Sekerka, J., Osterberg, E., Abbott, M.~B., Finney, B.~P., and Burns, S.~J.: Stable Isotope Records from Mount Logan, Eclipse Ice Cores and Nearby Jellybean Lake. Water Cycle of the North Pacific Over 2000 Years and Over Five Vertical Kilometres: Sudden Shifts and Tropical Connections, G\'{e}ogr. phys. Quatern., 58, 337,
doi:\href{http://dx.doi.org/10.7202/013147ar}{10.7202/013147ar}, 2004.

@@

\bibitem[{Kienast and McKay(2001)}]{Kienast.McKay.2001}
Kienast, S.~S. and McKay, J.~L.: Sea surface temperatures in the subarctic northeast Pacific reflect millennial-scale climate oscillations during the last 16 kyrs, Geophys. Res. Lett., 28, 1563--1566,
doi:\href{http://dx.doi.org/10.1029/2000GL012543}{10.1029/2000GL012543}, 2001.

@@

\bibitem[{Luckman and Osborn(1979)}]{Luckman.Osborn.1979}
Luckman, B. and Osborn, G.: Holocene glacier fluctuations in the middle Canadian Rocky Mountains, Quaternary Res., 11, 52--77,
doi:\href{http://dx.doi.org/10.1016/0033-5894(79)90069-3}{10.1016/0033-5894(79)90069-3}, 1979.

@@

\bibitem[{M\"{u}ller et~al.(1998)M\"{u}ller, Kirst, Ruhland, von Storch, and Rosell-Mel{\'{e}}}]{Muller.etal.1998}
M\"{u}ller, P.~J., Kirst, G., Ruhland, G., von Storch, I., and Rosell-Mel{\'{e}}, A.: Calibration of the alkenone paleotemperature index $U^{K'}_{37}$ based on core-tops from the eastern South Atlantic and the global ocean (60$^\circ$N-60$^\circ$S), Geochim. Cosmochim. Ac., 62, 1757--1772,
doi:\href{http://dx.doi.org/10.1016/s0016-7037(98)00097-0}{10.1016/s0016-7037(98)00097-0}, 1998.

@@

\bibitem[{Osborn et~al.(1995)Osborn, Clapperton, Davis, Reasoner, Rodbell, Seltzer, and Zielinski}]{Osborn.etal.1995}
Osborn, G., Clapperton, C., Davis, P., Reasoner, M., Rodbell, D.~T., Seltzer, G.~O., and Zielinski, G.: Potential glacial evidence for the younger dryas event in the Cordillera of North and South America, Quaternary Sci. Rev., 14, 823--832,
doi:\href{http://dx.doi.org/10.1016/0277-3791(95)00064-x}{10.1016/0277-3791(95)00064-x}, 1995.

@@

\bibitem[{Prahl and Wakeham(1987)}]{Prahl.Wakeham.1987}
Prahl, F.~G. and Wakeham, S.~G.: Calibration of unsaturation patterns in long-chain ketone compositions for palaeotemperature assessment, Nature, 330, 367--369,
doi:\href{http://dx.doi.org/10.1038/330367a0}{10.1038/330367a0}, 1987.

\bibitem[{Prahl et~al.(1988)Prahl, Muehlhausen, and Zahnle}]{Prahl.etal.1988}
Prahl, F.~G., Muehlhausen, L.~A., and Zahnle, D.~L.: Further evaluation of long-chain alkenones as indicators of paleoceanographic conditions, Geochim. Cosmochim. Ac., 52, 2303--2310,
doi:\href{http://dx.doi.org/10.1016/0016-7037(88)90132-9}{10.1016/0016-7037(88)90132-9}, 1988.

@@

\bibitem[{Reasoner et~al.(1994)Reasoner, Osborn, and Rutter}]{Reasoner.etal.1994}
Reasoner, M.~A., Osborn, G., and Rutter, N.~W.: Age of the Crowfoot advance in the Canadian Rocky Mountains: A glacial event coeval with the Younger Dryas oscillation, Geology, 22, 439--442,
doi:\href{http://dx.doi.org/10.1130/0091-7613(1994)022<0439:AOTCAI>2.3.CO;2}{10.1130/0091-7613(1994)022<0439:AOTCAI>2.3.CO;2}, 1994.

@@

\bibitem[{Shackleton(1967)}]{Shackleton.1967}
Shackleton, N.: Oxygen Isotope Analyses and Pleistocene Temperatures Re-assessed, Nature, 215, 15--17,
doi:\href{http://dx.doi.org/10.1038/215015a0}{10.1038/215015a0}, 1967.

@@

\bibitem[{Taylor et~al.(2015)Taylor, Hendy, and Pak}]{Taylor.etal.2015}
Taylor, M.~A., Hendy, I.~L., and Pak, D.~K.: The California Current System as a transmitter of millennial scale climate change on the northeastern Pacific margin from 10 to 50 ka, Paleoceanography, 30, 1168--1182,
doi:\href{http://dx.doi.org/10.1002/2014pa002738}{10.1002/2014pa002738}, 2015.
